Comparing top performing models

### 2019-04-02 Scripts/evaluating_models_with_dist_preds.Rmd
edits to results scripts

>>>>

```{r}
all_perfs <- rbind.data.frame(all_None_perfs,
                              all_ROS_perfs,
                              all_RUS_perfs,
                              all_smote_perfs)
all_perfs$Resampling <- c(rep("None",24),
                          rep("ROS",24),
                          rep("RUS",24),
                          rep("SMOTE",24))
all_perfs$CL <- factor(all_perfs$CL, levels=c("GM12878","K562"))
all_perfs$Resolution <- factor(all_perfs$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
all_perfs$Metric <- factor(all_perfs$Metric, levels=c("Balanced Acc", "F1-Score", "MCC"))
all_perfs$Resampling <- factor(all_perfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))

#gm12878
p1 <- ggplot(all_perfs[which(all_perfs$CL=="GM12878"),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
    geom_line(size=2)+
    geom_point(size=5)+
    facet_grid(~ Metric)+
    theme_minimal() +
    theme_bw()+
    xlab("") + ylab("") +
    ggtitle("GM12878") +
  scale_color_discrete(name="Re-Sampling Technique")+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
	                                 ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
	      plot.title = element_text(size=20))

#k562
p2 <- ggplot(all_perfs[which(all_perfs$CL=="K562"),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
    geom_line(size=2)+
    geom_point(size=5)+
    facet_grid(~ Metric)+
    theme_minimal() +
    theme_bw()+
    xlab("") + ylab("") +
    ggtitle("K562") +
  scale_color_discrete(name="Re-Sampling Technique")+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
	                                 ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
	      plot.title = element_text(size=20))

figure <- ggarrange(p1,p2,ncol = 2, nrow=1, common.legend = TRUE, legend = "top")
figure
annotate_figure(figure,
    bottom = text_grob("Resolution", color = "black", size = 20),
    left = text_grob("Performance", color = "black", rot = 90, size=20)
)
